---
title: "SDL_HYDRA_All"
author: "Delin Sun"
date: "4/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```
Statistical analyses of HYDRA outputs (by Delin Sun, Duke University, 04/16/2021)
The whole pipeline of the HYDRA project:
(1) Resting-state fMRI mean time series were extracted from 14 ROIs, which are in fact ICA-derived networks from FindLab.
(2) R-to-Z transformed Pearson's Correlation Coefficients between the time series from each pair of ROIs were calculated as features.
(3) All features (N=91) were harmonized to remove Site effects while keeping the information associated with bioogically relevant variables including disgnosis, age, and sex.
(4) Features + raw label of diagnosis (-1=controls, 1=patients) as well as covariates (age, age^2, sex) were entered into HYDRA to remove the effects of covariates and then cluster the patients into subgroups. The output ARI value was used to select the optimal number of subgroups. The output new labels separated patients into subgroups.
(5) This script aims to do the statistical analyses on HYDRA outputs to delineate their associations with demographic and clinical information.
```


```{r,include=FALSE}
# packages
library(tidyverse) # data manipulation and visualization
library(lme4) # for linear mixed regression models
library(lmerTest)# for p-value of lme4's models
library(ggplot2)
library(reshape2)
library(ggsci)
library(RColorBrewer) # for some extra colours in one of the graphs
library(table1) # make Table 1, mainly demographic & clinical info
library(sjPlot) # plot interactions of lm/lmer outputs
library(ggpubr) # plot multiple panels
library(forcats) # reorder the factors for plot

# library(ggpubr) # make easily publication ready plots
# library(rstatix) # pipe-friendly R functions for easy statistical analyses

# library(rayshader) # 2D plots to 3D plots
```

```{r,include=FALSE}
#######################################################################
# a function to plot heatmap for matrix of coefficients or p-values
# Input
# --- x, a vector, e.g. Pval0['Group',]
# --- title, title of the coclor bar, e.g. 'P-val (FDR corr.)'
# --- fmidpoint, mid point of the color bar, e.g. 0.05
# --- flimit, min and max of the color bar, e.g. c(0,1)
# Output
# --- a heatmap representing the input matrix
SDL_mheat <- function(x,title='Pearson Correlation',fmidpoint=0,flimit=c(-1,1)){
  # corr. coef. matrix
  n <- 14 # 14 ROIs from FindLab
  m <- matrix(data=0, nrow=n, ncol=n)
  m[lower.tri(m, diag=FALSE)] <- x
  m <- t(m)
  m[lower.tri(m, diag=FALSE)] <- x
  
  roinames <- c("anterior_Salience","Auditory","Basal_Ganlia","dDMN","high_Visual","Language","LECN","post_Salience","Precuneus","prim_Visual","RECN","Sensorimotor","vDMN","Visuospatial")
  rownames(m) <- roinames
  colnames(m) <- roinames

  # ggplot2 shows heatmap
  mm <- melt(m)
  # head(mm)
  mm %>% ggplot(aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = fmidpoint, limit = flimit, space = "Lab", name=title) +theme_minimal()+ theme(axis.text.x =element_text(angle = 45, vjust = 1, size = 12, hjust = 1))+coord_fixed()
}
##############################################################################
```


# Demographic and Clinical Info
```{r,echo=FALSE}
df0 <- read.csv("..\\Output\\timeseries_MDDPTSD\\All_harmonized.csv",header=T,sep=",")

# define factors
df0$Sex      <- df0$Sex %>% as.factor() %>% plyr::revalue(c("2"="Female", "1"="Male"))

df0$Group    <- df0$Group %>% as.factor() %>% plyr::revalue(c("-1"="Control","1"="MDD","2"="PTSD"))

df0$NewGroup <- df0$NewGroup %>% as.factor() %>% plyr::revalue(c("-1"="Control", "1"="PAT1","2"="PAT2"))

df0$NewGroup4 <- df0$NewGroup4 %>% as.factor() %>% plyr::revalue(c("-1"="Control", "1"="MDD1","2"="MDD2","3"="PTSD1","4"="PTSD2"))

df0          <- df0 %>% mutate(Group=fct_relevel(Group,"Control","PTSD"),NewGroup=fct_relevel(NewGroup,"Control","PAT1","PAT2"),NewGroup4=fct_relevel(NewGroup4,"Control","MDD1","MDD2","PTSD1","PTSD2"),Sex=fct_relevel(Sex,"Male","Female")) # reorder the levels of each factor

df0$Site <- df0$SITE %>% as.factor()
```



### Mean & SD per group (old labels)
```{r}
df <- df0 # just to keep df0 untouched
df %>% group_by(Group) %>% get_summary_stats(Age, type = "mean_sd")
```

### Number of subjects per group (old labels)
```{r}
df <- df0
df %>% group_by(Group,Sex) %>% summarise(n=n())
```

### heatmap of the corr. coef. in a sample subject
```{r}
# df_data[1,2:92] %>% as.numeric() %>% SDL_mheat(title='Pearson\nCorr. Coef.', fmidpoint=0, flimit=c(-1,1))
```

### Nean & SD per group (new labels)
```{r}
df <- df0 # just to keep df0 untouched
dfx <- df %>% group_by(NewGroup) %>% get_summary_stats(Age, type = "mean_sd")
dfx
aov(Age ~ NewGroup, data = df) %>% summary()
```

### Number of subjects per group (new labels)
```{r}
df <- df0 # just to keep df0 untouched
dfx <- df %>% group_by(NewGroup,Sex) %>% summarise(n=n())
dfx
dfx$n %>% matrix(2,3) %>% chisq.test()
```

### Number of subjects, group_by(NewGroup,Site)
```{r}
df <- df0
df1 <- df %>% group_by(NewGroup,Site) %>% summarise(n=n())
df1 %>% ggplot(aes(fill=NewGroup, y=n, x=Site, label=n)) + geom_bar(position="stack", stat="identity") +ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
m <- matrix(df1$n,5,3) %>% t() # Control, PAT1, & PAT2
m <- m[2:3,] # PTSD1 & PTSD2, or PTSD1 & PTSD2
m %>% chisq.test() # Pearson's Chi-squared Test for Count Data

```

### Number of subjects, group_by(NewGroup,Datasets)
```{r}
df <- df0
df$Datasets <- df0$SITE %>% as.factor() %>% plyr::revalue(c("1"="MDDSite", "2"="MDDSite","3"="MDDSite", "4"="MDDSite","5"="MDDSite", "6"="PTSDSite","7"="PTSDSite","8"="PTSDSite","9"="PTSDSite","10"="PTSDSite"))
df1 <- df %>% group_by(NewGroup,Datasets) %>% summarise(n=n())
df1 %>% ggplot(aes(fill=NewGroup, y=n, x=Datasets, label=n)) + geom_bar(position="stack", stat="identity") +ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
m <- matrix(df1$n,2,3) %>% t() # Control, PAT1, & PAT2
m <- m[2:3,] # PTSD1 & PTSD2, or PTSD1 & PTSD2
m %>% chisq.test() # Pearson's Chi-squared Test for Count Data

```




### Age, group_by(NewGroup,Site)
```{r}
df <- df0
df %>% group_by(NewGroup,Site) %>% get_summary_stats(Age, type = "mean_sd")
df %>% ggplot(aes(x=Site, y=Age, fill=NewGroup)) + geom_boxplot() + xlab("Site") + ylab("Age (Years)")
aov(Age ~ SITE * NewGroup, data = df) %>% summary()
```

### Current PTSD severity, group_by(NewGroup,Site)
```{r}
# dfx$CurrentPTSDSeverity <- dfx$Current.PTSD.severity %>% as.numeric()
# dfx %>% group_by(NewGroup,SITE) %>% get_summary_stats(CurrentPTSDSeverity, type = "mean_sd")
# dfx %>% ggplot(aes(x=SITE, y=CurrentPTSDSeverity, fill=NewGroup)) + geom_boxplot() + xlab("Site") + ylab("Current PTSD Severity")
```


### Recur, group_by(NewGroup,Recur)
```{r}
df <- df0[complete.cases(df0$Recur),] # remove rows with NaN
df$Recur <- df$Recur %>% as.factor()
df %>% group_by(NewGroup,Recur) %>% summarise(n=n())
df1 <- df %>% group_by(NewGroup,Recur) %>% summarise(n=n())
df1 %>% ggplot(aes(fill=Recur, y=n, x=NewGroup, label=n)) + geom_bar(position="stack", stat="identity") + ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
res <- prop.test(x=c(28,38),n=c(28+68,38+68)) # two-proportions z-test
res
# prop.test(x=df$Recur, n=df$Group, p = NULL, alternative = "two.sided", correct = TRUE)
```


### AD, group_by(NewGroup,AD)
```{r}
df <- df0[complete.cases(df0$AD),] # remove rows with NaN
df$AD <- df$AD %>% as.factor()
df %>% group_by(NewGroup,AD) %>% summarise(n=n())
df1 <- df %>% group_by(NewGroup,AD) %>% summarise(n=n())
df1 %>% ggplot(aes(fill=AD, y=n, x=NewGroup, label=n)) + geom_bar(position="stack", stat="identity") + ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
res <- prop.test(x=c(8,13),n=c(93+8,95+13)) # two-proportions z-test
res
```

### Rem, group_by(NewGroup,Rem)
```{r}
df <- df0[complete.cases(df0$Rem),] # remove rows with NaN
df$Rem <- df$Rem %>% as.factor()
df %>% group_by(NewGroup,Rem) %>% summarise(n=n())
df1 <- df %>% group_by(NewGroup,Rem) %>% summarise(n=n())
df1 %>% ggplot(aes(fill=Rem, y=n, x=NewGroup, label=n)) + geom_bar(position="stack", stat="identity") + ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
res <- prop.test(x=c(26,13),n=c(26+130,13+131)) # two-proportions z-test
res
```

### AO, group_by(NewGroup)
```{r}
df <- df0[complete.cases(df0$AO),] # remove rows with NaN
df1 <- df %>% group_by(NewGroup) %>% get_summary_stats(AO, type = "mean_sd")
df %>% ggplot(aes(x=NewGroup, y=AO, fill=NewGroup)) + geom_violin() + xlab("NewGroup") + ylab("AO")
```

### Sev, group_by(NewGroup,Sev)
```{r}
df <- df0[complete.cases(df0$Sev),] # remove rows with NaN
df$Sev <- df$Sev %>% as.factor()
df1 <- df %>% group_by(NewGroup,Sev) %>% summarise(n=n())
df1
df1 %>% ggplot(aes(fill=Sev, y=n, x=NewGroup, label=n)) + geom_bar(position="stack", stat="identity") + ylab("Number of Participants") + geom_text(size=3, position=position_stack(vjust = 0.5))
matrix(c(1,45,26,1,46,29),3,2) %>% chisq.test() # Pearson's Chi-squared Test for Count Data
```


```{r}
#######################################################################
# a function to model (lm or lmer) data for each ROI-to-ROI connection, and extract models/coefficients/p-values of models
# Input
# --- y, dataframe column, e.g. df$col01, or select(col1:col10)
# --- df, dataframe
# --- Otype, the type of outputs, e.g. "model", "coef", and "p"
# --- ftxt, text for the formula, e.g. "lmer(formula = y ~ age_d + age_m + drinking_class + sex + race + ses + fh_alc_density + life_trauma_RP + (1|participant_id)"
# --- fterms, which factor to be plotted
# --- fxy, x and y labels
# Output
# --- model, list of models
# --- coef,  matrix of coefficients
# --- pval,  matrix of coefficients
# --- plt,   list of plotting objects
SDL_lm <- function(y,df,Otype,ftxt,fterms=NULL,fxy=NULL){
  model <- eval(parse(text=paste(substr(ftxt,1,nchar(ftxt)-1),", data = df)")))
  coef  <- model %>% summary() %>% coefficients() # Estimate, Std. Error, t value, Pr(>|t|)
  tval  <- coef %>% .[,"t value"] 
  pval  <- coef %>% .[,"Pr(>|t|)"]
  #plt   <- model %>% plot_model(type = "pred", terms = fterms, title = "", axis.title = fxy)
  switch(Otype,"model"=return(model),"coef"=return(list(coef)),"tval"=return(tval),"pval"=return(pval),"plt"=return(list(plt)))
}
##############################################################################
```

# Between-group comparisons

## Raw group labels 
```{r,echo=FALSE}
NameGroupEffect <- 'GroupMDD'
NameGroupAge    <- 'GroupPTSD:Age'
NameGroupSex    <- 'GroupPTSD:SexFemale'

df <- df0
# patients vs. control
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0[NameGroupEffect,]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0[NameGroupEffect,])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Group:Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Age + Sex)")
x <- Tval0[NameGroupAge,]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0[NameGroupAge,])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Age in a sample connection
y <- df[,"V42"]
mod <- lm(formula = y ~ Group * Age + Sex, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Age","Group"), title = "dDMN-to-prim_Visual FC",axis.title=c("Age (Years)","rsFC")) # example plot of Group:Age effect

# scatter plots rsFC~Group:Age
df %>% ggplot(aes(x=Age, y=df[,"V42"], color=NewGroup, shape=Site)) + geom_point(size=2) + xlab("Age (Years)") + ylab("rsFC") + labs(title="dDMN-to-prim_Visual FC")


# Effect of Group:Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Sex + Age)")
x <- Tval0[NameGroupSex,]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Sex + Age)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0[NameGroupSex,])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Sex in a sample connection
y <- df[,"V56"]
mod <- lm(formula = y ~ Group * Sex + Age, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Group","Sex"), title = "LECN-to-Language FC",axis.title=c("NewGroup","rsFC")) # example plot of Group:Sex effect

# scatter plots rsFC~Group:Sex
df %>% ggboxplot(x="NewGroup", y="V56", color="Sex") + xlab("NewGroup") + ylab("rsFC") + labs(title="LECN-to-Language FC")
```



# New groups: (PAT1 + Controls) 
```{r,echo=FALSE}
# PTSD1 vs. controls
df <- df0 %>% filter(NewGroup!="PAT2") # only groups -1 & 1
df$Group <- df$NewGroup %>% as.character() %>% as.factor() # remove the level of PTSD2
# df %>% SDL_mplt()

# PTSD vs. control
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['GroupPAT1',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT1',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Group:Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Age + Sex)")
x <- Tval0['GroupPAT1:Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT1:Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Age in a sample connection
y <- df[,"V42"]
mod <- lm(formula = y ~ Group * Age + Sex, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Age","Group"), title = "dDMN-to-prim_Visual FC",axis.title=c("Age (Years)","rsFC")) # example plot of Group:Age effect

# scatter plots rsFC~Group:Age
df %>% ggplot(aes(x=Age, y=df[,"V42"], color=NewGroup)) + geom_point(size=2) + xlab("Age (Years)") + ylab("rsFC") + labs(title="dDMN-to-prim_Visual FC")


# Effect of Group:Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Sex + Age)")
x <- Tval0['GroupPAT1:SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Sex + Age)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT1:SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Sex in a sample connection
y <- df[,"V56"]
mod <- lm(formula = y ~ Group * Sex + Age, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Group","Sex"), title = "LCEN-to-Language FC",axis.title=c("NewGroup","rsFC")) # example plot of Group:Sex effect

# scatter plots rsFC~Group:Sex
df %>% ggboxplot(x="NewGroup", y="V56", color="Sex") + xlab("NewGroup") + ylab("rsFC") + labs(title="LCEN-to-Language FC")
```



## New groups: (PAT2 + Controls)
```{r,echo=FALSE}
# PAT2 vs. controls
df <- df0 %>% filter(NewGroup!="PAT1") # only groups -1 & 2
df$Group <- df$NewGroup %>% as.character() %>% as.factor() # remove the level of PTSD1
# df %>% SDL_mplt()

# PAT vs. control
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['GroupPAT2',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Group:Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Age + Sex)")
x <- Tval0['GroupPAT2:Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2:Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Age in a sample connection
y <- df[,"V42"]
mod <- lm(formula = y ~ Group * Age + Sex, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Age","Group"), title = "dDMN-to-prim_Visual FC",axis.title=c("Age (Years)","rsFC")) # example plot of Group:Age effect

# scatter plots rsFC~Group:Age
df %>% ggplot(aes(x=Age, y=df[,"V42"], color=NewGroup)) + geom_point(size=2) + xlab("Age (Years)") + ylab("rsFC") + labs(title="dDMN-to-prim_Visual FC")


# Effect of Group:Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Sex + Age)")
x <- Tval0['GroupPAT2:SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Sex + Age)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2:SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Sex in a sample connection
y <- df[,"V56"]
mod <- lm(formula = y ~ Group * Sex + Age, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Group","Sex"), title = "LECN-to-Language FC",axis.title=c("NewGroup","rsFC")) # example plot of Group:Sex effect

# scatter plots rsFC~Group:Sex
df %>% ggboxplot(x="NewGroup", y="V56", color="Sex") + xlab("NewGroup") + ylab("rsFC") + labs(title="LECN-to-Language FC")
```



## New groups: (PAT1 + PAT2)
```{r,echo=FALSE}
# PAT1 vs. PAT2
df <- df0 %>% filter(NewGroup!="Control") 
df$Group <- df$NewGroup %>% as.character() %>% as.factor() # remove the level of Control
# df %>% SDL_mplt()

# PAT2 vs. PAT1
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['GroupPAT2',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# Effect of Group:Age
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Age + Sex)")
x <- Tval0['GroupPAT2:Age',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2:Age',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Age in a sample connection
y <- df[,"V42"]
mod <- lm(formula = y ~ Group * Age + Sex, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Age","Group"), title = "dDMN-to-prim_Visual FC",axis.title=c("Age (Years)","rsFC")) # example plot of Group:Age effect

# scatter plots rsFC~Group:Age
df %>% ggplot(aes(x=Age, y=df[,"V42"], color=NewGroup)) + geom_point(size=2) + xlab("Age (Years)") + ylab("rsFC") + labs(title="dDMN-to-prim_Visual FC")


# Effect of Group:Sex
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group * Sex + Age)")
x <- Tval0['GroupPAT2:SexFemale',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group * Sex + Age)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPAT2:SexFemale',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

# plot the effects of Group:Sex in a sample connection
y <- df[,"V56"]
mod <- lm(formula = y ~ Group * Sex + Age, data=df)
# mod %>% summary()
mod %>% plot_model(type = "pred", terms = c("Group","Sex"), title = "LECN-to-Language FC",axis.title=c("NewGroup","rsFC")) # example plot of Group:Sex effect

# scatter plots rsFC~Group:Sex
df %>% ggboxplot(x="NewGroup", y="V56", color="Sex") + xlab("NewGroup") + ylab("rsFC") + labs(title="LECN-to-Language FC")
```








## New group4: (MDD1 + PTSD1)
```{r,echo=FALSE}
# MDD1 vs. MDD2
df <- df0 %>% filter(NewGroup4=="MDD1" | NewGroup4=="PTSD1") 
df$Group <- df$NewGroup4 %>% as.character() %>% as.factor() # remove the level of Control
# df %>% SDL_mplt()

# PAT2 vs. PAT1
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['GroupPTSD1',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPTSD1',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

```

## New group4: (MDD2 + PTSD2)
```{r,echo=FALSE}
# MDD2 vs. PTSD2
df <- df0 %>% filter(NewGroup4=="MDD2" | NewGroup4=="PTSD2") 
df$Group <- df$NewGroup4 %>% as.character() %>% as.factor() # remove the level of Control
# df %>% SDL_mplt()

# PTSD2 vs. MDD2
Tval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="tval", ftxt="lm(formula = y ~ Group + Age + Sex)")
x <- Tval0['GroupPTSD2',]
SDL_mheat(x=x, title='T-value', fmidpoint=0, flimit=c(min(x),max(x)))

Pval0 <- df %>% select(V1:V91) %>% sapply(SDL_lm, df=df, Otype="pval", ftxt="lm(formula = y ~ Group + Age + Sex)")  %>% t() %>% as.data.frame() %>% sapply(p.adjust,method="fdr") %>% t()
x <- -1* log10(Pval0['GroupPTSD2',])
SDL_mheat(x=x, title='-1*log10(P_FDR)', fmidpoint=-1*log10(0.05), flimit=c(min(x),max(x)))

```
